An Innovative Storage Stack Addressing Extreme Scale Platforms and Big Data Applications

### 2014-05-13 paper.tex
added NFS reference and fixed attribute notion error.

Other file systems, like GoogleFS~\cite{ghemawat:googlefs}, address distributed
rather than parallel computing and cannot be compared directly. The primary
difference between distributed and parallel file systems is the ability of the
file system to store and retrieve data simultaneously from multiple clients, in
parallel, and treat the resulting collection of pieces as a single object.
Distributed file systems rely on a single client creating a file, but
distributing the set of files across a wide array of storage devices. The
other, popular distributed file system of note is
HDFS~\cite{Shvachko:2010:hdfs} that is distributed as part of Hadoop. These
other file systems are mainly of interest in the context of the ACG features of
FFSIO and will be discussed more in Section~\ref{sec:acg}.

@@

Functionally, a container plays the same role as a file in that it holds a
collection of presumably related data intended to be accessed and manipulated
as a unit. Since this is extended from HDF5 files, the container could also be
viewed as a directory tree of objects where each directory entry specifies
either a sub-directory (group) or some data or attribute.

\subsubsection{Key-Value Store}
This is the base type for the container. Since the container represents
something akin to HDF5 files, everything is stored within a hierarchical
namespace. The root namespace is represented by the base key-value store and
contains a list of all of the objects for this portion of the namespace as well
as additional key-value objects representing sub-groups for the hierarchy. Each
of those key-value store objects works identically.

Attributes are stored in a key-value store object, but use the
multi-dimensional array and blob objects to store the values for the
attributes.

>>>>

Other file systems, like GoogleFS~\cite{ghemawat:googlefs} and
HDFS~\cite{Shvachko:2010:hdfs}, address distributed rather than parallel
computing and cannot be compared directly. The primary difference between
distributed and parallel file systems is the ability of the file system to
store and retrieve data simultaneously from multiple clients, in parallel, and
treat the resulting collection of pieces as a single object.  Distributed file
systems rely on a single client creating a file, but distributing the set of
files across a wide array of storage devices. The other, popular distributed
file system of note is NFS~\cite{powlowski:1994:nfs3} that has been used for
decades for enterprise file systems.  These other file systems are mainly of
interest in the context of the ACG features of FFSIO and will be discussed more
in Section~\ref{sec:acg}.

@@

Functionally, a container plays the same role as a file in that it holds a
collection of presumably related data intended to be accessed and manipulated
as a unit. Since this is extended from HDF5 files, the container could also be
viewed as a directory tree of objects where each directory entry specifies
either a sub-directory (group) or some data or attribute. For the IOD layer, it
is a collection of objects. For HDF5, interpreting the objects builds the
structure.

\subsubsection{Key-Value Store}
This is the base type for the container. Since the container represents
something akin to HDF5 files, everything is stored within a hierarchical
namespace. The root namespace is represented by the base key-value store and
contains a list of all of the objects for this portion of the namespace as well
as additional key-value objects representing sub-groups for the hierarchy. Each
of those key-value store objects works identically.  Attributes are stored in a
key-value store object.
%, but use the
%multi-dimensional array and blob objects to store the values for the
%attributes.
